---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simpriord

<!-- badges: start -->
<!-- badges: end -->

Using Bayesian models with informative priors is a common strategy to deal with the limitations of
statistical analysis with small sample size.  The goal of this package is to facilitate simulations
of Bayesian models which incorporate previous data (i.e., pilot data, publicly available data, etc.)
as prior information.  The package is inspired by three key resources.

The first resource is the Error Structures and Hyperparameters section of Cheung & Szpak (2021):

  "Informative priors can influence the outcome of a model, especially if the data set is
   small. Here, our last case study aims to test:
    a) How different error structures and intra-population groups compare with each other
    b) How much could hyperparameters sway the SIMMs estimation
    c) What is considered a sufficient sample size that is robust enough to stand against
    poorly informed hyperparameters"

The second resource is paul.buerkner's first two posts in the Setting Informative Priors from
Pilot Study for Lognormal Model thread on the discourse.mc-stan.org forums (https://discourse.mc-stan.org/t/setting-informative-priors-from-pilot-study-for-lognormal-model/4741):

  "If you analyse your final data set including both data from pilot and main study, I wouldn’t let the       priors be informed too much by the data of the pilot study, because then you end up including this data    twice into your model (one as data and one as prior).

   If you have the raw data of previous studies available, I would usually prefer putting all data into the    same model (with extended structure) instead of trying to use the posterior of one study as prior of the    other. The latter is really hard to do correctly."
   
   "With extended structure I mean modeling that the data came from two different studies (e.g., via an        additional factor in the model) unless the studies are exact replications with samples from the same       populeation."
   
The third resource is Dr. Gregory L. Snow's simulation code posted in the [R-sig-ME] Poer Analysis for Multi-level Models thread on the stat.ethz.ch forums (https://stat.ethz.ch/pipermail/r-sig-mixed-models/2009q1/001790.html).

## Installation

You can install the development version of simpriord from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mncube/simpriord")
```

## Simulate from a linear model

Use the sim_lm function to simulate one data frame from a linear model.

```{r example}
library(simpriord)

lm_df <- sim_lm()

head(lm_df)
```


Use the sim_lm_dfs function to generate a list of data frames each of which contain main
and previous data.

```{r}
lm_dfs <- sim_lm_dfs(frames = 3,
                     mod_name = list("mod1", "mod2", "mod3"))

str(lm_dfs)

head(lm_dfs[[2]])

tail(lm_dfs[[2]])
```

## Citations

Cheung, C., & Szpak, P. (2021). Interpreting Past Human Diets Using Stable Isotope Mixing Models. In Journal of Archaeological Method and Theory (Vol. 28, Issue 4, pp. 1106–1142). https://doi.org/10.1007/s10816-020-09492-5
